On the Cram\'{e}r-Rao bound for polynomial phase signals

### 2013-07-09 paper.tex
minor

\usepackage{mathbf-abbrevs}

@@

We remark on our notation.  We use lowercase letters for working variables and we use Greek letters for fixed parameters.  Where possible we use the lowercase letter and its Greek counterpart when there is a relationship between a working variable and a fixed parameter.  For example we use $b=(b_0,\dots,b_m)$ as arguments to represent the polynomial phase coefficients in~\eqref{eq:polyestfunction}, and we use $\beta = (\beta_0, \dots \beta_m)$ to denote the fixed (true) unknown coefficients that we desire to estimate in~\eqref{eq:yndatamodel}.  It is common in the literature to use a subscript zero, for example $b_0$ to denote the true parameter, but this notation is confusing in our case since $b_0$ is also an element in the vector $b$.

@@

Figures~\ref{plot:phase0},~\ref{plot:phase1}~and~\ref{plot:phase2} represent a somewhat artificial situation, since when $m=2$ the $3 \times 3$ matrix $F$ is not poorly conditioned, and can be accurately inverted.  Our explanation for choosing $m=2$ in Figures~\ref{plot:phase0},~\ref{plot:phase1}~and~\ref{plot:phase2} is that it is not computationally feasible to compute the maximum likelihood estimator for $m>2$.  In practice, the matrix $F$ becomes difficult to invert when $m>5$.  For example, MATLAB warns of numerical imprecision when attempting to invert $F$ when $m>5$.  Figure~\ref{plot:relerror} displays the relative error of the approximate Cram\'{e}r-Rao bound for polynomial phase signals of order $m=8$.  The relative error is defined as $(\tilde{F}_{ii}^{-1} - F_{ii}^{-1})/F_{ii}^{-1}$ where $\tilde{F}_{ii}^{-1}$ is the approximate Cram\'{e}r-Rao bound given by equation (34) in~\cite{Peleg1991_CRB_PPS_1991}.  The relative error is larger for the lower order coefficients.  The relative error decreases as $N$ increases, but is still significant for the low order coefficients when $N=100$.

@@

\bibliographystyle{elsarticle-num}
\small 
\bibliography{bib}

>>>>

\usepackage{mathbf-abbrevs}
%\usepackage{setspace}

@@

We remark on our notation.  We use lowercase Roman letters for working variables and we use Greek letters for fixed parameters.  Where possible we use the lowercase Roman letter and its Greek counterpart when there is a relationship between a working variable and a fixed parameter.  For example we use $b=(b_0,\dots,b_m)$ as arguments to represent the polynomial phase coefficients in~\eqref{eq:polyestfunction}, and we use $\beta = (\beta_0, \dots \beta_m)$ to denote the fixed (true) unknown coefficients that we desire to estimate in~\eqref{eq:yndatamodel}.  It is common in the literature to use a subscript zero, for example $b_0$ to denote the true parameter, but this notation is confusing in our case since $b_0$ is also an element in the vector $b$.

@@

Figures~\ref{plot:phase0},~\ref{plot:phase1}~and~\ref{plot:phase2} represent a somewhat artificial situation, since when $m=2$ the $3 \times 3$ matrix $F$ is not poorly conditioned, and can be accurately inverted numerically.  Our explanation for choosing $m=2$ in Figures~\ref{plot:phase0},~\ref{plot:phase1}~and~\ref{plot:phase2} is that it is not computationally feasible to compute the maximum likelihood estimator for $m>2$.  In practice, the matrix $F$ becomes difficult to invert when $m>5$.  For example, MATLAB warns of numerical imprecision when attempting to invert $F$ when $m>5$.  Figure~\ref{plot:relerror} displays the relative error of the approximate Cram\'{e}r-Rao bound for polynomial phase signals of order $m=8$.  The relative error is defined as $(\tilde{F}_{ii}^{-1} - F_{ii}^{-1})/F_{ii}^{-1}$ where $\tilde{F}_{ii}^{-1}$ is the approximate Cram\'{e}r-Rao bound given by equation (34) in~\cite{Peleg1991_CRB_PPS_1991}.  The relative error is larger for the lower order coefficients.  The relative error decreases as $N$ increases, but is still significant for the low order coefficients when $N=100$.

@@

{
\bibliographystyle{elsarticle-num}
\tiny 
\bibliography{bib}
}
